Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-03-29 r_scripts/parallel_presentation.Rmd
revise

## Parallel on server
For loop vs Apply

@@

```
1. Forloop (one core, or not parallel computing)

```{r forloop, echo = FALSE}
start <- proc.time()
for (i in 201:310) {
  # output value of zipcode
  zipcode <- as.character(or_zip_name[i]) 
  # limit shapefile to particular zipcode
  zip_shape <- or_zip_map[or_zip_map$ZCTA5CE10 %in% zipcode, ]
  # convert to polygon
  zip_poly <-SpatialPolygons(zip_shape@polygons)
for(j in 201:300){
    # output each grid and create a polygon
    wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == j, ]
    # now what about grid 719; should be much less
    wrf_poly <- SpatialPolygons(wrf_grid@polygons)

@@

2. Mapply function (one core)

@@

}
proportion <- mapply(f3, rep(201:300, each=100), rep(201:300,100))
stop <- proc.time() - start
stop

@@

3. Mcmapply function in parallel computing (multiple cores)

@@

}
proportion <- mcmapply(f3, rep(201:300, each=100), rep(201:300,100))
stop <- proc.time() - start
stop

@@

>>>>

## Parallel on server
**For loop vs Apply**

@@

```
**1. Forloop** (one core, or not parallel computing)

```{r forloop, echo = FALSE}
start <- proc.time()
for (i in 1:417) {
  # output value of zipcode
  zipcode <- as.character(or_zip_name[i]) 
  # limit shapefile to particular zipcode
  zip_shape <- or_zip_map[or_zip_map$ZCTA5CE10 %in% zipcode, ]
  # convert to polygon
  zip_poly <-SpatialPolygons(zip_shape@polygons)
for(j in 1:1610){
    # output each grid and create a polygon
    wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == j, ]
    # now what about grid 719; should be much less
    wrf_poly <- SpatialPolygons(wrf_grid@polygons)

@@

**2. Mapply function** (one core)

@@

}
proportion1 <- mapply(f3, rep(1:417, each=1610), rep(1:1610,417))
stop <- proc.time() - start
stop

@@

**One core vs Multiple cores**

**3. Mcmapply function** in parallel computing (multiple cores)

@@

}
proportion <- mcmapply(f3, rep(1:417, each=1610), rep(1:1610,417))
stop <- proc.time() - start
stop

@@

Another important thing:
Check if they are identical!
```{r, echo=FALSE}
## write matrix of for loop formed
zip_proportion_df <- data.frame(zip_wrf_proportion)

write_path <- paste0('../../../data/data_new/',
                     'zip_wrf_proportion2.csv')
write_csv(zip_proportion_df, paste0(write_path))

## write matrix of apply function formed
zip_wrf_proportion_new <- matrix(proportion, nrow = 417, ncol = 1610, byrow = T,
                                    dimnames = list(or_zip_name, wrf_grid_name))

zip_proportion_new_df <- data.frame(zip_wrf_proportion_new)
write_path <- paste0('../../../data/data_new/',
                     'zip_wrf_proportion_new2.csv')
write_csv(zip_proportion_new_df, paste0(write_path))

read_path_1 <- paste0('../../../data/data_new/',
                     'zip_wrf_proportion2.csv')
zip_wrf_proportion_for <- read_csv(read_path_1)
read_path_2 <- paste0('../../../data/data_new/',
                     'zip_wrf_proportion_new2.csv')
zip_wrf_proportion_apply <- read_csv(read_path_2)

identical(zip_wrf_proportion_for, zip_wrf_proportion_apply)
